Graph Generators: State of the Art and Open Challenges

### 2019-06-16 challenges.tex
Reviewer's comments - part I.

\subsection{Multi-model Data}
With the dawn of Big Data and especially its Variety, another key 3V characteristic, new types of
database management systems have emerged. One of the most interesting ones
are the so-called \emph{multi-model databases} that enable to store and
thus query across structurally different data. There exist various types of
multi-model systems combining  distinct subsets of Big Data structures including graph data.
For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
implemented on the basis of an object DBMS currently supports graph, document,
key/value, and object models. Such type of DBMSs also needs a specific
data generator that would enable
to test new features and analyze efficiency of operations. However, since the
multi-model systems are in the context of Big Data rather new, there exist only
a few benchmarks targeting multi-model DBMSs (such as
Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
with limited capabilities.

>>>>

\subsection{Multi-model Data}
With the dawn of Big Data and especially its Variety, another key 3V characteristic, new types of
database management systems have emerged. One of the most interesting ones
are the so-called \emph{multi-model databases} that enable to store and
thus query across structurally different data, including structured, semi-structured, and unstructured. There exist various types of
multi-model systems combining  distinct subsets of Big Data structures including graph data.
For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
implemented on the basis of an object DBMS currently supports graph, document,
key/value, and object models. Such type of DBMSs also needs a specific
data generator that would enable
to test new features and analyze efficiency of operations. However, since the
multi-model systems are in the context of Big Data rather new, there exist only
a few benchmarks targeting multi-model DBMSs (such as
Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
with limited capabilities.

### 2019-06-16 comparison.tex
Reviewer's comments - part I.

At first we classify the generators on the basis of the respective application domains or user communities. In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data steaming. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

@@

If we consider the features of the particular domain of the generators, in most cases it is expectably fixed. It is the simplest option, but it does mean that the generator is simple too -- it can still focus on other complex aspects of the output. The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas. They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP~\cite{dblp} or DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}). Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven/pattern-driven domain or a domain extracted from sample data.

@@

As we have mentioned, the basic classification that we have used in this paper
is  based on a relatively vague division of the generators on the basis of the
current application domains or research areas. In addition, some of the
generators are either general or have features applicable in other domains. So
the classes can overlap, as depicted in Table~\ref{tab:overlapping}.

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{3}{*}{\rot{\textbf{Co}}}
  & Danon et al. & x & & & & x & {\bf x} &\\
\cline{2-9}
  & LFR & x & & & & x & {\bf x} & \\
\cline{2-9}
  & LFR-Overlapping & x & & & & x & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

In the case of LinkBench, nothing prevents the user to load the generated graph
in a graph database (Facebook uses MySQL in that paper) to
test a workload similar to Facebook and extend and complement it with more
graph queries like those in LDBC-SNB.

>>>>

At first we classify the generators on the basis of the respective application domains or user communities. In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data streaming. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

@@

If we consider the features of the particular domain of the generators, in most cases it is expectably \emph{fixed}, i.e., it is pre-defined (describing, e.g., a social network) and cannot be modified. It is the simplest option, but it does mean that the generator is simple too -- it can still focus on other complex aspects of the output. While the \emph{schema-driven} approaches enable to influence the target domain using a user-supplied schema, there also exist approaches where the domain is \emph{extracted} from sample data. The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas. They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP~\cite{dblp} or DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}). Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven/pattern-driven domain or a domain extracted from sample data.

@@

As we have mentioned, the basic classification of the generators that we have used in this paper is relatively vaguely based on the current application domains or research areas. In addition, some of the generators are either general, and thus can be used universally, or have features applicable in more than one domain/research area. So the classes we use can overlap, as depicted in Table~\ref{tab:overlapping}.

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Streaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{3}{*}{\rot{\textbf{Co}}}
  & Danon et al. & x & & & & x & {\bf x} &\\
\cline{2-9}
  & LFR & x & & & & x & {\bf x} & \\
\cline{2-9}
  & LFR-Overlapping & x & & & & x & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

In the case of LinkBench, nothing prevents the user to load the generated graph
in a (graph) database (e.g., Facebook uses MySQL in~\cite{Armstrong:2013:LDB:2463676.2465296}) to
test a workload similar to Facebook and extend and complement it with more
graph queries like those in LDBC-SNB.

### 2019-06-16 generators_LinkedData.tex
Reviewer's comments - part I.

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties~\cite{Guo2005158}. In addition, the LUBM benchmark provides 14 test queries. In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the instance data over ontologies, as an opposite to \emph{intentional} queries, i.e., queries which target the properties and  classes of the ontology. The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., the first university is named \emph{University0} and so on), thus they are reproducible at any time with the same indexes.  The generator allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.

>>>>

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties~\cite{Guo2005158}. In addition, the LUBM benchmark provides 14 test queries. In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology. The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., the first university is named \emph{University0} and so on), thus they are reproducible at any time with the same indexes.  The generator allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.
